Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-06-10 paper/paper.tex
more more fixes

% official NIPS keywords
\textbf{\\keywords}: systems biology, mind-wandering, cognitive science,
artificial intelligence, Markov decision process
\textbf{XXX: Maybe the keywords "systems biology" and "cognitive science" are too broad. I would also remove "reinforcement learning", which is already in the title. The keywords are the occasion to enhance reachability through web and bibliography search. What about "process model", "Markov decision processes", or "Bellman equation"?}
% autonomous learning systems
% \textbf{\\Get opinion from}: Danielle Bassett, Kai Vogeley, Mohammad Shakir,
% Guillaume Dumas, Smallwood, Tenenbaum

>>>>

% official NIPS keywords
\textbf{\\keywords}: mind-wandering, artificial intelligence, Markov decision process

% autonomous learning systems
% \textbf{\\Get opinion from}: Danielle Bassett, Kai Vogeley, Mohammad Shakir,
% Guillaume Dumas, Smallwood, Tenenbaum
